A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-07 paper/ms.tex
update ms

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.3\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler satellite because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show that
  Kepler\,1627 is a member of the \clusterage\ old $\delta$~Lyr
  cluster using kinematic information from Gaia, stellar rotation
  periods from TESS, and Li abundances from ground-based spectra.  To
  our knowledge, Kepler\,1627Ab is the youngest planet with a precise
  age yet found by the main Kepler mission.  From unresolved
  starspot-crossing events in the Kepler photometry and
  a Keck/HIRES transit we find that the planet is likely on an
  orbit aligned with the stellar spin axis.  We also briefly explore the flare
  arrival time distribution in the short cadence Kepler
  photometry.
  The $\delta$~Lyr cluster is one of many stellar groups whose
  properties have been clarified using the Gaia data; many other new
  clusters also overlap with confirmed and candidate exoplanets.
  Verifying the results of Gaia clustering analyses using TESS rotation
  periods seems likely to be a path toward expanding the census of
  age-dated planets, and our understanding of planetary evolution.
\end{abstract}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f15c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf The \cn\ is \clusterage\ old.}  {\it Top:}
    Color-magnitude diagram of the \cn, IC\,2602 ($\approx35$\,Myr),
    the Pleiades ($\approx 115$\,Myr; \citealt{dahm_2015}), and the
    Gaia EDR3 Catalog of Nearby Stars (gray background density;
    log-stretch).  The right panel provides a zoomed view of stars on
    the pre-main-sequence.  The \cn\ and IC\,2602 are approximately
    the same isochronal age.  {\it Bottom:} TESS and Kepler stellar
    rotation periods versus dereddened Gaia colors, with the Pleiades
    and Praesepe (650\,Myr) shown for reference
    \citep{rebull_rotation_2016a,douglas_poking_2017}.  The \cn\ is
    gyrochronally younger than the Pleiades.
   \label{fig:age}
	}
\end{figure*}

@@

		\subfloat{
			\includegraphics[width=\textwidth]{f5.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The full Kepler dataset spans 1{,}437 days (3.9 years), sampled at
    30 minute cadence.  A one hundred day segment is shown here.  The
    {\it top panel} shows the \texttt{PDCSAP} median-subtracted flux
    in units of parts-per-thousand ($\times 10^{-3}$).  The dominant
    signal is induced by starspots.  The model for the stellar
    variability (orange line) is subtracted below, revealing the
    transits of \pn, as well as other deviations from the
    model.  The Figure Set online shows the
    entire 3.9 years of observations.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627Ab, with stellar variability
    removed.  The 2-$\sigma$ model uncertainties and the maximum {\it
    a posteriori} model are shown as the faint purple band, and the
    dark purple line.  Gray points are individual \texttt{PDCSAP} flux
    measurements; black points are binned to 20 minutes, with a
    representative error bar shown.  The asymmetric residual visible
    during the transit is robust against detrending methods; we
    believe it is caused by starspot crossings.
    \label{fig:lc}
  }
\end{figure*}

@@

		\subfloat{
			\includegraphics[width=0.49\textwidth]{f16.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
    {\it Top:} 
    The time of each Kepler transit was measured, along with the local
    slope of the light curve.  The two quantities appear
    anti-correlated, which is most easily explained by starspot
    crossings during the first (second) half of transit inducing a
    positive (negative) TTV, provided that the orbit is prograde
    \citep{mazeh_time_2015}.  The units along the abscissa are most
    easily understood by considering that the flux from the star
    changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
    {\it Bottom:} Radial velocities from Keck/HIRES during a transit
    on 7 Aug 2021 UT, observed simultaneously with MuSCAT3 ({\it griz}
    photometry).  A quadratic baseline trend was allowed in the RV
    fit.  The best-fit sky-projected obliquity in this model is listed
    in red; the detection however has marginal statistical
    significance compared to a ``trend-only'' model.
    \label{fig:obliquity}
	}
\end{figure}

@@

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  More
precise observations of the Doppler transit could yield a more precise
stellar obliquity, and a means for verifying the expected prograde
orbit.  Similar transit
spectroscopy aimed at detecting either hydrogen or helium absorption
could yield insight into the stability of the planet's atmosphere
\citep[{\it e.g.},][]{spake_helium_2018,vissapragada_2020}.  A more
challenging measurement would be to determine the planet's mass,
either through detailed timing analyses of the Kepler data, or through
a high-cadence multi-color radial velocity campaign.  The mass,
measured at sufficient precision, could yield constraints on both the
planet's composition as well as its initial entropy
\citep{owen_constraining_2020}.

The precision of the Kepler data itself may enable more detailed
analyses without needing to acquire more data.  While our transit
timing study did not yield the detection of any clearly significant
planet-planet induced TTVs, the star's flaring may be suggestive of
star-planet interactions.  Appendix~\ref{app:flare} highlights an odd
flare timing coincidence that may be worthy of further examination.

In the context of the known transiting planets, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages below 100\,Myr include K2-33b, DS~Tuc~Ab,
HIP~67522b, TOI~837b, AU~Mic~b, and the four-planet V1298~Tau system
\citep{Mann_K2_33b_2016,David_et_al_2017,newton_tess_2019,david_four_2019,bouma_cluster_2020,plavchan_planet_2020}.
\pn\ is currently the smallest of these systems ($\approx
3.3\,R_\oplus$), which may hint at selection effects in the young
planet sample \citep{zhou_2021_tois}.  Assuming that these planets
have masses between $\approx$5$\,M_\oplus$ and 10$\,M_\oplus$, their
large sizes and presumed low densities are in accord with the
expectation that mini-Neptunes start their lives with large primordial
atmospheres that are shed over the first gigayear
\citep{Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018}.  Our
suggestion of an aligned orbit differs from observed misalignments in
number of other close-in
mini-Neptunes~\citep{sanchis-ojeda_starspots_2011,albrecht_obliquities_2012,dalal_2019_hd3167,rubenzahl_tess-keck_2021}.
Unlike these older planets, \pn\ seems to have properties
consistent with a quiescent disk-driven migration history.  The
alternative scenario of in-situ formation is disfavored on theoretical
grounds: the required disk mass would likely drive migration, and so
lacks internal consistency
\citep{inamdar_formation_2015,ogihara_reassessment_2015}.

Ultimately, the main advance of this work was a precise measurement of
the age of \pn.   This age measurement was enabled by identifying the
connection of the star to the \cn\ using the Gaia data.  Table~\ref{tab:v06}
should enable similar crossmatches to
already known planets, as well as forthcoming planets from the TESS
mission \citep{ricker_transiting_2015,guerrero_tess_2021}.  An
alternative path toward age-dating more planets could be to identify kinematic associations
around known exoplanet host stars using positions and tangential velocities
from Gaia, and to then verify these associations with ancilliary
rotation periods and spectroscopy \citep[{\it e.g.},][]{tofflemire_tess_2021}.

@@

\software{
  %\texttt{arviz} \citep{arviz_2019},
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  %\texttt{astroplan} \citep{astroplan2018},
	%\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
  \texttt{astropy} \citep{astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  %\texttt{ceres} \citep{brahm_2017_ceres},
  %\texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019},
  \texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  dependencies \citep{exoplanet:agol20, exoplanet:kipping13, exoplanet:luger18,
   	exoplanet:theano},
	%\texttt{gala} \citep{gala,PriceWhelan_2017_gala_zenodo},
	%\texttt{IDL Astronomy User's Library} \citep{landsman_1995},
  \texttt{IPython} \citep{perez_2007},
	%\texttt{isochrones} \citep{morton_2015_isochrones},
	%\texttt{lightkurve} \citep{lightkurve_2018},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  %\texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  %\texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  %\texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{TESS-point}  \citep{burke_2020},
  %\texttt{tesscut} \citep{brasseur_astrocut_2019},
	%\texttt{VESPA} \citep{morton_efficient_2012,vespa_2015},
  %\texttt{webplotdigitzer} \citep{rohatgi_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}
\

@@

The \texttt{v0.6} CDIPS target catalog (Table~\ref{tab:v06}) includes
some important updates from previous versions.  As in
\citet{bouma_cdipsI_2019}, we collected membership information for
young, age-dated, or age-dateable stars from across the literature.
Table~\ref{tab:metadata} gives a list of the sources included, and
some brief summary statistics.

The first major important change is that the extent of analyses
performed on the Gaia data at the time of our compilation was wide and
deep enough that we opted to neglect pre-Gaia analyses, except in
cases for which spectroscopically confirmed samples of stars had been
collected.  The membership lists for instance of
\citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014} (MWSC and
DAML) were no longer required, especially given their relatively high
field-star contamination rates compared to Gaia-derived membership
catalogs.

For any of the catalogs for which Gaia DR2 identifiers were not
immediately available, we either followed the spatial (plus
proper-motion) crossmatching procedures described in
\citet{bouma_cdipsI_2019}, or else we pulled the Gaia DR2 source
identifiers associated with the catalog from SIMBAD.  We consequently
opted to drop the $\texttt{ext\_catalog\_name}$ and $\texttt{dist}$
columns maintained in \citet{bouma_cdipsI_2019}, as these were only
populated for a small number of stars.

The most crucial parameters of a given star for our purposes are the
Gaia DR2 source identifier ($\texttt{source\_id}$), the cluster name
($\texttt{cluster}$), and the ($\texttt{age}$).  Given the
hierarchical nature of many stellar associations, we do not attempt to
resolve the cluster names to a single unique string.  The Orion
complex for instance, can be divided into almost one hundred kinematic
subgroups \citep{kounkel_apogee2_2018}.  Similar complexity applies to
the problem of determining homogeneous ages, which we do not attempt
to resolve.  Instead, we simply merged the cluster names and ages
reported by various authors together.

This means that our ``age'' column can be null, for cases in which the
original authors did not report an age, and a reference literature age
was not readily available.  Nonetheless, since we do generally prefer
stars with known ages, we made a few additional efforts to populate
this column.  When available, the age provenance is from the original
analysis of the cluster.  However, in a few cases we adopted other
ages when the string-based crossmatches on the ``cluster'' name was
straightforward.  In particular, we used the ages determined by
\citet{CantatGaudin2020b} to assign ages to the catalogs from
\citet{GaiaCollaboration2018}, \citet{CantatGaudin2018a},
\citet{CastroGinard2020}, and \citet{CantatGaudin2020a}.

The catalogs we included for which ages were not immediately available
were those of \citet{CottenSong2016}, \citet{Oh2017},
\citet{Zari2018}, \citet{Gagne2018a},
\citet{Gagne2018b},\citet{Gagne2018c}, and \citet{Ujjwal2020}.  While
in principle the moving group members discussed by
\citet{Gagne2018a,Gagne2018b,Gagne2018c} and \citet{Ujjwal2020} have
easily associated ages, our SIMBAD cross-matching lost the moving
group association from those studies, which should therefore be
recovered tools such as BANYAN
$\Sigma$.\footnote{\url{http://www.exoplanetes.umontreal.ca/banyan/banyansigma.php}}.
We also included the SIMBAD object identifiers $\texttt{TT*}$,
$\texttt{Y*O}, $\texttt{Y*?}, $\texttt{TT?}$, and $\texttt{pMS*}$.
Finally, we also included every star in the NASA Exoplanet Archive
$\texttt{ps}$ table that had a Gaia identifier available
\citep{NASAExoArchive_ps_20210506}.  If the age had finite
uncertainties, we also included it, since stellar ages determined
through the combination of isochrone-fitting and transit-derived
stellar densities typically have higher precision than from isochrones
alone.

The technical manipulations for the merging, cleaning, and joining
were performed using $\texttt{pandas}$
\citep{mckinney-proc-scipy-2010}.  The eventual crossmatch (using the
Gaia DR2 $\texttt{source\_id}$) against the Gaia DR2 archive was performed
asychronously on the Gaia archive
website\footnote{\url{https://gea.esac.esa.int/archive/}}.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f15supp.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf Binarity indicators for rotators in \cn.} 
    Data are as in the lower panel of
    Figure~\ref{fig:age}.  Astrometric binaries ($\mathrm{RUWE}>1.2$)
    appear in red; photometric binaries ($>$0.3\,mag above an
    empirical isochrone; 20\% of stars) are orange.  
    Over $0.6<\bpmrpo<1.5$, the detected rotation periods in binaries tend to 
    fall below the slow sequence.
    %FIXME!
		% Over $0.5<\bpmrpo<1.3$, Set $\mathcal{B}$ has \replaced{281}{523} stars.
		% Dividing these stars into ``slow'' and ``fast'' sequences by eye,
		% the fraction of stars showing signs of binarity in the slow and fast
		% subsamples are \replaced{30\% (63/210)}{27\% (106/289)} and
		% \replaced{56\% (40/71)}{51\% (68/134)}, respectively.
		\label{fig:binarity}
	}
\end{figure}

@@

\subsection{Long Cadence Data}
\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f9.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Transit model residuals through time (binned by Kepler quarter)}.  
    {\it Left:}
    Phase-folded transit of Kepler 1627b, with stellar variability
    removed.  Black points are binned to 20
    minute intervals.  The 2-$\sigma$ model uncertainties and the
    maximum {\it a posteriori} model are shown as the faint purple
    band, and the dark purple line.
    {\it Right:}
    As on the left, with the transit removed.  Quarters 6 and 7 show a
    consistent deviation in the second half of the transit.
		\label{fig:phasequarter}
	}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f10.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Transit model residuals through time (binned by year of observation)}.  
    {\it Left:}
    Phase-folded transit of Kepler 1627b, with stellar variability
    removed.  Points and models are as
    in Figure~\ref{fig:phasequarter}.
    {\it Right:}
    As on the left, with the transit removed.
		\label{fig:phaseyear}
	}
\end{figure}

@@

Our adopted model therefore included 10 free parameters for the
transit ($\{P,t_0,\log R_{\rm p}/R_\star,b,u_1,u_2,R_\star, \log g,
e\cos\omega, e\sin\omega \}$), 2 parameters for the light curve
normalization and uncertainty calibration ($\{\langle f \rangle,  \log
\sigma_f \}$), and 5 hyperparameters for the GP
($\{\sigma_{\mathrm{rot}}, \log P_{\mathrm{rot}}, \log Q_0, \log
\mathrm{d}Q, f \}$).  We also considered including an additive
\texttt{SHOTerm} kernel to account for stochastic noise, but found
that this did not significantly affect the results, and so opted for
the simpler GP kernel.  We fitted the models using \texttt{PyMC3}
\citep{salvatier_2016_PyMC3,exoplanet:theano}.  After initializing
each model with the parameters of the maximum {\it a posteriori}
model, we assumed a Gaussian likelihood, and sampled using
\texttt{PyMC3}'s gradient-based No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014}. We used $\hat{R}$ as our convergence
diagnostic \citep{gelman_inference_1992}.

>>>>

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.3\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler satellite because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show that
  Kepler\,1627 is a member of the \clusterage\ old $\delta$~Lyr
  cluster, based on Gaia kinematics, TESS stellar rotation
  periods, and spectroscopic lithium abundances.  To
  our knowledge, Kepler\,1627Ab is the youngest planet with a precise
  age yet found by the main Kepler mission.  From unresolved
  starspot-crossing events in the Kepler photometry and
  a Keck/HIRES transit we find that the planet is likely on an
  orbit aligned with the stellar spin axis.  We also briefly explore the flare
  arrival time distribution in the short cadence Kepler
  photometry.
  The $\delta$~Lyr cluster is one of many stellar groups whose
  properties have been clarified using Gaia; many other new
  clusters also overlap with confirmed and candidate exoplanets.
  Verifying the results of Gaia clustering analyses using TESS rotation
  periods seems to be a promising path toward expanding the census of
  age-dated planets, and our corresponding understanding of planetary evolution.
\end{abstract}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f15c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf The \cn\ is \clusterage\ old.}  {\it Top:}
    Color-magnitude diagram of the \cn, IC\,2602 ($\approx38$\,Myr),
    the Pleiades ($\approx 115$\,Myr; \citealt{dahm_2015}), and the
    Gaia EDR3 Catalog of Nearby Stars (gray background;
    log-stretch).  The right panel is a zoomed view of 
    the pre-main-sequence.  The \cn\ and IC\,2602 are approximately
    the same isochronal age.  {\it Bottom:} TESS and Kepler stellar
    rotation periods versus dereddened Gaia colors, with the Pleiades
    and Praesepe (650\,Myr) shown for reference
    \citep{rebull_rotation_2016a,douglas_poking_2017}.  Most of the
    candidate \cn\ members are gyrochronally younger than the
    Pleiades.
   \label{fig:age}
	}
\end{figure*}

@@

		\subfloat{
			\includegraphics[width=\textwidth]{f5.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The full Kepler dataset spans 1{,}437 days (3.9 years), sampled at
    30 minute cadence.  A one hundred day segment is shown here.  The
    top panel shows the \texttt{PDCSAP} median-subtracted flux in
    units of parts-per-thousand ($\times 10^{-3}$).  The dominant
    signal is induced by starspots.  The model for the stellar
    variability (orange line) is subtracted below, revealing the
    transits of \pn, as well as other deviations from the model.  The
    Figure Set online shows the entire 3.9 years of observations.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627Ab, with stellar variability
    removed.  The 2-$\sigma$ model uncertainties and the maximum {\it
    a posteriori} model are shown as the faint purple band, and the
    dark purple line.  Gray points are individual \texttt{PDCSAP} flux
    measurements; black points are binned to 20 minutes, with a
    representative error bar shown.  The asymmetric residual visible
    during the transit is robust against detrending methods; we
    believe that it is caused by starspot crossings.
    \label{fig:lc}
  }
\end{figure*}

@@

		\subfloat{
			\includegraphics[width=0.49\textwidth]{f16.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
    {\it Top:} 
    The time of each Kepler transit was measured, along with the local
    slope of the light curve.  The two quantities appear
    anti-correlated, which is most easily explained by starspot
    crossings during the first (second) half of transit inducing a
    positive (negative) TTV, provided that the orbit is prograde
    \citep{mazeh_time_2015}.  The units along the abscissa are most
    easily understood by considering that the stellar flux
    changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
    {\it Bottom:} Radial velocities acquired using Keck/HIRES during
    the transit of 7 Aug 2021 UT, observed simultaneously with MuSCAT3
    ({\it griz} photometry).  A quadratic baseline trend was allowed
    in the RV fit.  The best-fit sky-projected obliquity in this model
    is listed in red; the detection however has marginal statistical
    significance compared to a ``trend-only'' model.
    \label{fig:obliquity}
	}
\end{figure}

@@

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  More precise
observations of the Doppler transit could yield a more precise stellar
obliquity, and a means for verifying the expected prograde orbit.
Similarly, transit spectroscopy aimed at detecting either hydrogen or
helium absorption could yield insight into the stability of the
planet's atmosphere \citep[{\it
e.g.},][]{spake_helium_2018,vissapragada_2020}.  A more challenging
measurement would be to determine the planet's mass, either through
detailed timing analyses of the Kepler data, or through a high-cadence
multi-color radial velocity campaign.  Measured at
sufficient precision, the mass could yield constraints on both the
planet's composition as well as its initial entropy
\citep{owen_constraining_2020}.

Separately, the Kepler data may still contain further information.
Although our transit timing study did not yield the detection of any
clearly significant planet-planet TTVs, the star's flaring may be
suggestive of star-planet interactions.  Appendix~\ref{app:flare}
highlights an odd flare timing coincidence that may be worthy of
further examination.

In the context of the known transiting planets, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages below 100\,Myr include K2-33b, DS~Tuc~Ab,
HIP~67522b, TOI~837b, AU~Mic~b, and the four-planet V1298~Tau system
\citep{Mann_K2_33b_2016,David_et_al_2017,newton_tess_2019,david_four_2019,bouma_cluster_2020,plavchan_planet_2020}.
\pn\ is currently the smallest of these systems ($\approx
3.3\,R_\oplus$), which may hint at selection effects in the young
planet sample \citep{zhou_2021_tois}.  Assuming that these planets
have masses between $\approx$5$\,M_\oplus$ and 20$\,M_\oplus$, their
large sizes and presumed low densities would be in accord with the
expectation that mini-Neptunes start their lives with large primordial
atmospheres that are shed over the first gigayear
\citep{Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018}.  Our
suggestion of an aligned orbit differs from observed misalignments in
number of other close-in
mini-Neptunes~\citep{sanchis-ojeda_starspots_2011,albrecht_obliquities_2012,dalal_2019_hd3167,rubenzahl_tess-keck_2021}.
Unlike these older planets, \pn\ seems to have properties
consistent with a quiescent disk-driven migration history.  The
alternative scenario of in-situ formation is disfavored on theoretical
grounds: the required disk mass would likely drive migration, and so
lacks internal consistency
\citep{inamdar_formation_2015,ogihara_reassessment_2015}.

Ultimately, the main advance of this work was a precise measurement of
the age of \pn.   This age measurement was enabled by identifying the
connection of the star to the \cn\ using the Gaia data.  Table~\ref{tab:v06}
should enable similar cross-matches to
already known planets, as well as forthcoming planets from the TESS
mission \citep{ricker_transiting_2015,guerrero_tess_2021}.  An
alternative path toward age-dating more planets could be to identify kinematic associations
around known exoplanet host stars using positions and tangential velocities
from Gaia, and to then verify these associations with ancilliary
rotation periods and spectroscopy \citep[{\it e.g.},][]{tofflemire_tess_2021}.

@@

\software{
  %\texttt{arviz} \citep{arviz_2019},
  \texttt{altaipony} \citep{ilin_flares_2021},
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  %\texttt{astroplan} \citep{astroplan2018},
	%\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
  \texttt{astropy} \citep{astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  %\texttt{ceres} \citep{brahm_2017_ceres},
  %\texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019},
  \texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  dependencies \citep{exoplanet:agol20, exoplanet:kipping13, exoplanet:luger18,
   	exoplanet:theano},
	%\texttt{gala} \citep{gala,PriceWhelan_2017_gala_zenodo},
	%\texttt{IDL Astronomy User's Library} \citep{landsman_1995},
  \texttt{IPython} \citep{perez_2007},
	%\texttt{isochrones} \citep{morton_2015_isochrones},
	%\texttt{lightkurve} \citep{lightkurve_2018},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  %\texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  %\texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  %\texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{TESS-point}  \citep{burke_2020},
  %\texttt{tesscut} \citep{brasseur_astrocut_2019},
	%\texttt{VESPA} \citep{morton_efficient_2012,vespa_2015},
  %\texttt{webplotdigitzer} \citep{rohatgi_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}
\

@@

The \texttt{v0.6} CDIPS target catalog (Table~\ref{tab:v06}) includes
stars that are young, age-dated, and age-dateable.  By ``age-dateable'',
we mean that the age should be measurable at greater
precision than a typical FGK field star.
As in
\citet{bouma_cdipsI_2019}, we collected stars that met these criteria
from across the literature.  Table~\ref{tab:metadata} gives a list of
the studies included, and some brief summary statistics.
The age measurement approaches adopted by each study differ: in many,
spatial and kinematic clustering has been performed on the Gaia data,
and ensemble isochrone fitting of the cluster has been performed
(typically focusing on the turn-off).
In others however, the claim of youth is based on the location of a
single star in the color-magnitude diagram, or on spectroscopic
information.

One major change in Table~\ref{tab:v06} relative to the analogous
table from \citet{bouma_cdipsI_2019} is that the extent of Gaia-based
analyses has now matured to the point that we can neglect pre-Gaia
cluster memberships, except for a few cases with spectroscopically
confirmed samples of age-dated stars.  The membership lists for
instance of \citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014}
(MWSC and DAML) are no longer required.  This is helpful for various
post-processing projects,  since the field-star contamination rates
were typically much higher than analogous Gaia-based cluster membership
catalogs.

The most crucial parameters of a given star for our purposes are the
Gaia DR2 $\texttt{source\_id}$, the cluster or
group name ($\texttt{cluster}$), and the $\texttt{age}$.  Given the
hierarchical nature of many stellar associations, we do not attempt to
resolve the cluster names to a single unique string.  The Orion
complex for instance can be divided into almost one hundred kinematic
subgroups \citep{kounkel_apogee2_2018}.  Similar complexity applies to
the problem of determining homogeneous ages, which we do not attempt
to resolve.  Instead, we simply merged the cluster names and ages
reported by various authors into a comma-separated string.

This means that our \texttt{age} column can be null, for cases in
which the original authors did not report an age, and a reference
literature age was not readily available.  Nonetheless, since we do
generally prefer stars with known ages, we made a few additional
efforts to populate this column.  When available, the age provenance
is from the original analysis of the cluster.  In a few cases
however we adopted other ages when string-based cross-matches on the
cluster name was straightforward.  In particular, we used the ages
determined by \citet{CantatGaudin2020b} to assign ages to the catalogs
from \citet{GaiaCollaboration2018}, \citet{CantatGaudin2018a},
\citet{CastroGinard2020}, and \citet{CantatGaudin2020a}.

The catalogs we included for which ages were not immediately available
were those of \citet{CottenSong2016}, \citet{Oh2017},
\citet{Zari2018}, \citet{Gagne2018b},
\citet{Gagne2018a}, \citet{Gagne2018c}, and \citet{Ujjwal2020}.  While
in principle the moving group members discussed by
\citet{Gagne2018b,Gagne2018a,Gagne2018c} and \citet{Ujjwal2020} have
easily associated ages, our SIMBAD cross-match lost the moving group
identifiers given by those studies, which should therefore be recovered
tools such as BANYAN
$\Sigma$.\footnote{\url{http://www.exoplanetes.umontreal.ca/banyan/banyansigma.php}}.
We also included the SIMBAD object identifiers $\texttt{TT*}$,
$\texttt{Y*O}, $\texttt{Y*?}, $\texttt{TT?}$, and $\texttt{pMS*}$.
Finally, we  included every star in the NASA Exoplanet Archive
$\texttt{ps}$ table that had a Gaia identifier available
\citep{NASAExoArchive_ps_20210506}.  If the age had finite
uncertainties, we also included it, since stellar ages determined
through the combination of isochrone-fitting and transit-derived
stellar densities typically have higher precision than from isochrones
alone.

For any of the catalogs for which Gaia DR2 identifiers were not
immediately available, we either followed the spatial (plus
proper-motion) cross-matching procedures described in
\citet{bouma_cdipsI_2019}, or else we pulled the Gaia DR2 source
identifiers associated with the catalog from SIMBAD.  We consequently
opted to drop the $\texttt{ext\_catalog\_name}$ and $\texttt{dist}$
columns maintained in \citet{bouma_cdipsI_2019}, as these were only
populated for a small number of stars.
The technical manipulations for the merging, cleaning, and joining
were performed using $\texttt{pandas}$
\citep{mckinney-proc-scipy-2010}.  The eventual cross-match (using the
Gaia DR2 $\texttt{source\_id}$) against the Gaia DR2 archive was
performed asychronously on the Gaia archive
website\footnote{\url{https://gea.esac.esa.int/archive/}}.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.7\textwidth]{f15supp.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf Binarity indicators for rotators in \cn.} 
    Data are as in the lower panel of
    Figure~\ref{fig:age}.  Astrometric binaries ($\mathrm{RUWE}>1.2$)
    appear in red; photometric binaries ($>$0.3\,mag above an
    empirical isochrone; 20\% of stars) are orange.  
    Over $0.6<\bpmrpo<1.5$, the detected rotation periods in binaries tend to 
    fall below the slow sequence.
    %FIXME!
		% Over $0.5<\bpmrpo<1.3$, Set $\mathcal{B}$ has \replaced{281}{523} stars.
		% Dividing these stars into ``slow'' and ``fast'' sequences by eye,
		% the fraction of stars showing signs of binarity in the slow and fast
		% subsamples are \replaced{30\% (63/210)}{27\% (106/289)} and
		% \replaced{56\% (40/71)}{51\% (68/134)}, respectively.
		\label{fig:binarity}
	}
\end{figure}

@@

\subsection{Long Cadence Data}
\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.64\textwidth]{f9.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Transit model residuals through time (binned by Kepler quarter)}.  
    {\it Left:}
    Phase-folded transit of Kepler 1627b, with stellar variability
    removed.  Black points are binned to 20
    minute intervals.  The 2-$\sigma$ model uncertainties and the
    maximum {\it a posteriori} model are shown as the faint purple
    band, and the dark purple line.
    {\it Right:}
    As on the left, with the transit removed.  Quarters 6 and 7 show a
    consistent deviation in the second half of the transit.
		\label{fig:phasequarter}
	}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.64\textwidth]{f10.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Transit model residuals through time (binned by year of observation)}.  
    {\it Left:}
    Phase-folded transit of Kepler 1627b, with stellar variability
    removed.  Points and models are as
    in Figure~\ref{fig:phasequarter}.
    {\it Right:}
    As on the left, with the transit removed.
		\label{fig:phaseyear}
	}
\end{figure}

@@

Our model therefore included 10 free parameters for the
transit ($\{P, t_0, R_{\rm p}/R_\star, b, u_1 ,u_2 ,R_\star, \log g,
e, \omega \}$), 2 parameters for the light curve
normalization and uncertainty calibration ($\{\langle f \rangle, 
\sigma_f \}$), and 5 hyperparameters for the GP
($\{\sigma_{\mathrm{rot}}, P_{\mathrm{rot}}, Q_0,
\mathrm{d}Q, f \}$).  We also considered including an additive
\texttt{SHOTerm} kernel to account for stochastic noise, but found
that this did not significantly affect the results, and so opted for
the simpler GP kernel.  We fitted the models using \texttt{PyMC3}
\citep{salvatier_2016_PyMC3,exoplanet:theano}.  After initializing
each model with the parameters of the maximum {\it a posteriori}
model, we assumed a Gaussian likelihood, and sampled using
\texttt{PyMC3}'s gradient-based No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014} in these bases indicated in Table~\ref{tab:posterior}.
We used $\hat{R}$ as our convergence
diagnostic \citep{gelman_inference_1992}.
